Playing against Nature: causal discovery for decision making under uncertainty

### 2018-05-22 Segundo_Semestre/CausalML_Workshop/Paper_long_version.tex
Correcciones Sucar: abstract

\[ \frac{1}{B(\alpha)}  \prod_{i=1}^k x_i^{\alpha-1},\]

@@

For the second case, we must consider both the occurrences of that data point as well as the parents for each of the variables. Following \cite{barber2012bayesian} we denote as $\theta_i(X,j)$ the probability $P(X=i | Pa(X)=j)$ In this case, if the prior of $X$ is given by a a Dirichlet($\alpha$), then the posterior for a variable $X$ with parents $Pa(X)$ and an observed data point is given by 
\[ \prod_j \textrm{Dirichlet}(\alpha + u(j)) \]
where $u(j)$ counts the number of times that in the data point the parents of $X$ had the value $j$.

@@

If we plot the average rewards obtained we observe they converge to 1 as shown in the next figure.

\begin{figure}[ht]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{/Users/MauricioGS1/INAOE/Segundo_Semestre/CausalML_Workshop/rewar.png}}
\caption{Average reward obtained by the decision maker in 50 rounds of the decision makin-belief updating cycle.}
\label{average_reward}
\end{center}
\vskip -0.2in
\end{figure}

@@

For this third case, we make an extra assumption: the maximum number of variables in the model is known to the decision maker. This allow to consider only distributions of fixed dimension. In this case we will consider distributions over matrixes of fixed size rather than vectors as in the previous case.

@@

The most notable difference with the previous case is that the \textit{structure} of the model is also to be learned in such a way that both the structure and parameters converge to the true model in the limit.

In the previous case the decision maker knew the form of the CPT's involved in any calculation. In this case, she doesn't know the structure of the DAG so which CPT's are involved is unknown.

If the decision maker knew exactly what variables are involved, even though she didn't know how they are connected, she could use a \textit{Dirichlet Process} to generate Dirichlet distributions and generate causal graphical models the same way as in case 2. The Dirichlet Process, which was introduced by \cite{ferguson1973bayesian}, is a stochastic process whose finite-dimensional distributions are Dirichlet random variables \cite{hjort2010bayesian}, \cite{ghosal2017fundamentals}. It is the most common \textit{nonparametric prior} in the context of Bayesian Nonparametrics.

Belief updating in this context is yet to be studied.

>>>>

\[ f(x_1,...,x_k | \alpha_i,...,\alpha_k)=\frac{1}{B(\alpha)}  \prod_{i=1}^k x_i^{\alpha_i-1},\]

@@

For the second case, we must consider both the occurrences of that data point as well as the parents for each of the variables. Following \cite{barber2012bayesian} we denote as $\theta_i(X,j)$ the number of times the event $\{X=i | Pa(X)=j\}$ is observed. In this case, if the prior of $X_i$ is given by a a Dirichlet($\alpha$), then the posterior for a variable $X_i$ with parents $Pa(X)$ and an observed data point is given by 
\[ \prod_j \textrm{Dirichlet}(\alpha + \theta_i(\cdot,j)). \]

@@

The agent obtained a total reward of $47$ out of $50$ posible points
\begin{figure}[ht]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{/Users/MauricioGS1/INAOE/Segundo_Semestre/CausalML_Workshop/rewar.png}}
\caption{Average reward obtained by the decision maker in 50 rounds of the decision makin-belief updating cycle.}
\label{average_reward}
\end{center}
\vskip -0.2in
\end{figure}

On the other hand, an agent that is randomly choosing one of the two treatment options obtains a reward of $37$ out of $50$ possible points

\begin{figure}[ht]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{/Users/MauricioGS1/INAOE/Segundo_Semestre/CausalML_Workshop/random_reward.png}}
\caption{Average reward obtained by the decision maker in 50 rounds of randomly choosing a treatment in the causal model.}
\label{random_reward}
\end{center}
\vskip -0.2in
\end{figure}

@@

@@

The most notable difference with the previous case is that the \textit{structure} of the model is also to be learned in such a way that both the structure and parameters converge to the true model in the limit. In the previous case the decision maker knew the form of the CPT's involved in any calculation. In this case, she doesn't know the structure of the DAG so which CPT's are involved is unknown.

If the decision maker knew exactly the variables that appear in the true model thar governs the environment, even though she didn't know how they are connected, she could use a \textit{Dirichlet Process} to generate Dirichlet distributions and generate causal graphical models the same way as in case 2. The Dirichlet Process\footnote{with parameters $M,G_0$}, which was introduced by \cite{ferguson1973bayesian}, is random measure defined over a space $S$ such that for each partition $B_1,...,B_k$ the vector $(G(B_1),...,G(B_k))$ follows a Dirichlet distribution \cite{hjort2010bayesian}, \cite{muller2016bayesian}, \cite{ghosal2017fundamentals}.

Belief updating using causal information is yet to be studied and left as future work.
